Stack Safety as a Security Property

### 2020-07-08 main.tex
Typo

  \item If the machine takes \emph{simultaneous return-call step}, that is, the
    instruction to which execution returns immediately after completing a call
    is itself a call instruction, the \emph{call step} and \emph{return step}
    cases are combined.

>>>>

  \item If the machine takes a \emph{simultaneous return-call step}, that is,
    the instruction to which execution returns immediately after completing a
    call is itself a call instruction, the \emph{call step} and \emph{return
    step} cases are combined.
